% -*-latex-*-
% 
% For questions, comments, concerns or complaints:
% thesis@mit.edu
% 
%
% $Log: cover.tex,v $
% Revision 1.8  2008/05/13 15:02:15  jdreed
% Degree month is June, not May.  Added note about prevdegrees.
% Arthur Smith's title updated
%
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach

% NOTE:
% These templates make an effort to conform to the MIT Thesis specifications,
% however the specifications can change.  We recommend that you verify the
% layout of your title page with your thesis advisor and/or the MIT 
% Libraries before printing your final copy.
\title{Fault Detection and Diagnosis for Drones using Machine Learning}

\author{Elgiz Baskaya}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\department{Applied Mathematics}

% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}
\degree{Doctor of Philisophy in Aeronautics and Astronautics}

% As of the 2007-08 academic year, valid degree months are September, 
% February, or June.  The default is June.
\degreemonth{February}
\degreeyear{2018}
\thesisdate{February 22, 2018}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{\copyright IBM, 1990.  Do not open till Xmas.}

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Daniel Delahaye}{Professor}
\supervisor{Murat Bronz}{Assistant Professor}

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{Arthur C. Smith}{Chairman, Department Committee on Graduate Theses}

% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle

% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.

%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.

% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}

% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}

\cleardoublepage

\section*{Acknowledgments}


First of all, I would like to thank to my PhD advisors, Professors Daniel Delahaye and Murat Bronz, for supporting me during these past three years. I am grateful to Daniel Delahaye, for his insight during the thesis and directed me to the very interesting topic of machine learning. I would like to thank Murat Bronz for initiating the PhD opportunity, his guidance throughout this thesis, his help for the modifications to the \emph{Paparazzi} autopilot and being the safety pilot during the flight campaigns. I would also like to thank  Stephane Puechmorel for his insight that lead to interesting results also discussed in this thesis.

The drone team in ENAC, Yannick Jestin (the best boss), Michel Gorraz, Fabian Garcia, Alexandre Bustico, Fabian Bonneval. You guys are great, it was such a pleasure..
Extra thanks for their help on flight campaigns to Torbjoern Cunis, Gauthier Hattenberger, and Michel Gorraz.
Special thanks to Torbjoern for even cooking me dinner during difficult times. 
And to the triple sec; Guido Manfredi and Jim Sharples; I am grateful to you for the all the shared moments and your endless support.
And the drone team is luckily even larger, I am so happy that we worked all together with Jean-Philippe Condomines, Xavier Paris, Titouan Verdu, Yuchen Leng, Baizura Bohari.
All colleagues and friends with whom my last three years has passed. BEST team ever. Felt like home. Thank you all..

My family, my mom Nergiz and father Adiguzel, I am grateful to you most, for the most precious gift you gave me, my life. 
Mom, you are the reason of my freedom, my imagination and my free will. I always admired you being competent since I first saw you at work, passionately talking on your profession, eyes closed, hard to believe that it was my mother. 
And dad, you are the reason for my artistic spirit, which tries to burst out of me sometimes. You both always supported me on music, always supported my choices, I was lucky to be grown as a free spirit, I think this is where I am grateful to you the most. 

My brother, you are really special to me. It is enough to make me happy just knowing you are there.

My grandmom, nananem. The cleverest women I have ever known, lucky to be raised by you. I wont forget that you being the person that I get along the best, never even an argument, like magic. My flees to captain's bridge has never been punished on the way along the sea to summer house, my never finishing questions never left unanswered, my passion for sea shells and flower seeds plugging the washing machines have been ignored. 

My uncle Cengiz, where my logic genes have been inherited. Again, the person I have never argued even once in my lifetime, no delays in communication, or may be sometimes when something else is been processed. The best person I have ever known in my life, an angel. Too clever, too talented. And my lovely aunt Leyla, who woke me up everyday, patiently, thank you many times.

Rapunzel, my companion, you have helped me a ton, you made me graduate. Although you wont be able to read it, you won't be the first one. 

Ertan, you have helped me numerous times I stopped counting, my crisis, my anxieties, my vulnerabilities. Those days I was about to quit, you made me back, not let me to leave Rapunzel, told me that I can do it, and I did it.

I also thank my friend, my sister, Hale, for providing support and friendship that I needed. 

Utku, ne 3 u la, my perfect lab mate. Hope to work AI together here or there, one day.. 

Estelle, I am thankful for what we have shared during three years, and grateful for her help, especially during the last phase of this thesis.

Helen, thanks to her, the paperwork which I hated with a passion became much of an ease. Such a nice person, kind, and gentle. Thank you very much.

I am also grateful to Sara, Micheal, and Magda for proofreading the thesis, and Sarah for her incredible illustrations and the cover of this thesis. 

This work is supported by ENGIE Ineo - Groupe ADP - Safran RPAS Chair. I am grateful for their support that enabled me to pursue three years of research on this interesting subject. I am also grateful to Catherine Ronfle-Nadaud for her support during the early stages of \emph{Chaire Drones}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -*-latex-*-
